Outline of Ideas for BTC Transaction Frequency

### 2015-10-05 outline/outline.tex
Added some preliminary results

@@

In this example simulation we assume that the transaction data process $x_t$ follows a continuous time random walk with drift with parameters $\mu$ and $\sigma$, that is
\[
x_t - x_s \sim N((t-s)\mu, (t-s)\sigma^2)
\]
for $t > s$. So $dx_t = \mu dt + \sigma d B_t$ where $B_t$ is Brownian motion. Using a simulation, Table \ref{tab:bmprob} contains Monte Carlo estimates of the probability that a block fills up under a variety of choices of $\mu$ and $\sigma$. The current average transaction data rate per minute  is $\mu=0.04$ MBs. As $\sigma$ increases the probability of a block filling increases, though when $\sigma$ is close to zero an increase in $\sigma$ may cause the probability to decrease slightly. For most of the range, however, increasing $\sigma$ increases the probability that a block fills up.

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Tue Sep 22 16:26:38 2015
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrrrr}
  \hline
 & $\sigma = 0$ & $\sigma = 0.001$ & $\sigma = 0.01$ & $\sigma = 0.1$ & $\sigma = 1$ & $\sigma = 10$ & $\sigma = 100$ & $\sigma = 1000$ \\ 
  \hline
$\mu = 0.035$ & 0.0594 & 0.0594 & 0.0597 & 0.0927 & 0.3574 & 0.4822 & 0.4979 & 0.4994 \\ 
  $\mu = 0.04$ & 0.0836 & 0.0835 & 0.0839 & 0.1149 & 0.3624 & 0.4824 & 0.4978 & 0.5005 \\ 
  $\mu = 0.045$ & 0.1098 & 0.1098 & 0.1103 & 0.1367 & 0.3680 & 0.4829 & 0.4977 & 0.4995 \\ 
  $\mu = 0.05$ & 0.1366 & 0.1366 & 0.1370 & 0.1596 & 0.3739 & 0.4837 & 0.4983 & 0.5003 \\ 
   \hline
\end{tabular}
\caption{Approximate probability of filling of a block under various choices of $\mu$ and $\sigma$.}
\label{tab:bmprob}
\end{table}

>>>>

Table \ref{tab:probsims} contains estimates of the probability of a filled block under a variety of assumptions, using parameter estimates of the posterior distribution of the model using 1000 contiguous blocks ending with block $253,221$ from August 20, 2013 arriving at about 11:39 a.m.
% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct  5 14:56:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
$\mu - \hat{\mu}$ & $P_{\bar{\mu}}$ & $P_{\mu^{(0.5)}}$ & $P_{\mathrm{post}}$ \\ 
  \hline
0 & 0.01 & 0.01 & 0.00 \\ 
  0.01 & 0.03 & 0.03 & 0.03 \\ 
  0.05 & 0.23 & 0.23 & 0.22 \\ 
  0.1 & 0.42 & 0.42 & 0.42 \\ 
  0.5 & 0.82 & 0.82 & 0.83 \\ 
   \hline
\end{tabular}
\caption{Estimated probability of a filled block under a variety of assumptions. From the posterior distribution the mean is $\bar{\mu} = 0.0179$ and the median is $\mu^{(0.5)} = 0.0174$. The value of $\mu - \hat{\mu}$ is the amount added to the estimated value of $\mu$ for the purposes of the simulation, $P_{\bar{\mu}}$ is the probability of a filled block using posterior means for parameter estimates, $P_{\mu^{(0.5)}}$ is the probability of a filled block using posterior medians, and $P_{\mathrm{post}}$ is the probability of a filled block using the full posterior distribution.}
\label{tab:probsims}
\end{table}

@@

In this example simulation we assume that the transaction data process $x_t$ follows a continuous time random walk with drift with parameters $\mu$ and $\sigma$, that is
\[
x_t - x_s \sim N((t-s)\mu, (t-s)\sigma^2)
\]
for $t > s$. So $dx_t = \mu dt + \sigma d B_t$ where $B_t$ is Brownian motion. Using a simulation, Table %\ref{tab:bmprob}
 contains Monte Carlo estimates of the probability that a block fills up under a variety of choices of $\mu$ and $\sigma$. The current average transaction data rate per minute  is $\mu=0.04$ MBs. As $\sigma$ increases the probability of a block filling increases, though when $\sigma$ is close to zero an increase in $\sigma$ may cause the probability to decrease slightly. For most of the range, however, increasing $\sigma$ increases the probability that a block fills up.

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Tue Sep 22 16:26:38 2015
%\begin{table}[ht]
%\centering
%\begin{tabular}{lrrrrrrrr}
%  \hline
% & $\sigma = 0$ & $\sigma = 0.001$ & $\sigma = 0.01$ & $\sigma = 0.1$ & $\sigma = 1$ & $\sigma = 10$ & $\sigma = 100$ & $\sigma = 1000$ \\ 
%  \hline
%$\mu = 0.035$ & 0.0594 & 0.0594 & 0.0597 & 0.0927 & 0.3574 & 0.4822 & 0.4979 & 0.4994 \\ 
%  $\mu = 0.04$ & 0.0836 & 0.0835 & 0.0839 & 0.1149 & 0.3624 & 0.4824 & 0.4978 & 0.5005 \\ 
%  $\mu = 0.045$ & 0.1098 & 0.1098 & 0.1103 & 0.1367 & 0.3680 & 0.4829 & 0.4977 & 0.4995 \\ 
%  $\mu = 0.05$ & 0.1366 & 0.1366 & 0.1370 & 0.1596 & 0.3739 & 0.4837 & 0.4983 & 0.5003 \\ 
%   \hline
%\end{tabular}
%\caption{Approximate probability of filling of a block under various choices of $\mu$ and $\sigma$%.}
%\label{tab:bmprob}
%\end{table}
